On first-order combinatorial proofs

### 2020-12-17 main.tex
Add the bibliography

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}
\usepackage{cmll}
\usepackage{tikz}

\parindent=0pt
\parskip=0.6em

@@

\subsection{{\bf LK}}
We start with Gentzen's sequent calculus system {\bf LK}.

@@

Consider the following deep rules:
\begin{center}
\mbox{
\begin{prooftree}
  \hypo{\vdash S\{A \vee A\}}
  \infer1[$\cD$]{\vdash S\{A\}}
\end{prooftree}
\hspace{2cm}

@@

D. Hughes proves the soundness and completeness of
unification nets with respect to {\bf MLL1} + $mix$. In the following, we establish the
equivalence between unification nets and fonets.

@@

\end{document}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}
\usepackage{cmll}
\usepackage{tikz}
\usepackage{natbib}

\parindent=0pt % indent spacing
\parskip=0.6em % spacing between two paragraphs
\setlength{\bibsep}{1.2ex} % bibliography vertical spacing

@@

\subsection{{\bf LK}}
We start with Gentzen's sequent calculus system {\bf LK} \cite{Gentzen 1935}.

@@

Consider the following deep rules \cite{BT 2001}:
\begin{center}
\mbox{
\begin{prooftree}
  \hypo{\vdash S\{A \vee A\}}
  \infer1[$\cD$]{\vdash S\{A\}}
\end{prooftree}
\hspace{2cm}

@@

D. Hughes proves in \cite{Hughes 2019} the soundness and completeness of
unification nets with respect to {\bf MLL1} + $mix$. In the following, we establish the
equivalence between unification nets and fonets.

@@

\input{bibliography}
\end{document}
